DOpElib:\\ Differential Equations and Optimization Environment

### 2019-04-24 Examples/PDE/StatPDE/Example16/content.tex
Fixed references and license

 Further, in this example we show a residual based error estimator
 for the obstacle problem, as given in~\cite{Walloth:2017}. In
 principle this is similar to the calculations needed in
 Example~\ref{PDE_adap_Stat_Laplace}, i.e., defining the
 \texttt{Strong*Residual} terms in the \texttt{LocalPDE} class.
 However, for the estimate of the obstacle we need too special
 information. First, for a given vertex $x_i$, we need to know if
 $x_i$ is a \textit{full contact} node, meaning that $u = \chi$ on
 $\omega_i = \cup_{T \mid x_i \in T} T$ the patch around $v$. Further,
 we need to have $|\omega_i| = \int_{\omega_i} \phi_i\,\mathrm{d}x$ for all
 vertices to correctly scale the complementarity residual.
 Unfortunately, both data are non-local, i.e., we can not compute it
 on any given $T$ alone.

>>>>

 Further, in this example we show a residual based error estimator
 for the obstacle problem, as given in~\cite{Walloth:2017}; see
 also~\cite{MoonNochettoPetersdorffZhang:2007,KrauseVeeserWalloth:2015} for the original idea for parabolic VIs and the analysis
 for a Signorini problem. In
 principle this is similar to the calculations needed in
 Example~\ref{PDE_adap_Stat_Laplace}, i.e., defining the
 \texttt{Strong*Residual} terms in the \texttt{LocalPDE} class.
 However, for the estimate of the obstacle we need too special
 information. First, for a given vertex $x_i$, we need to know if
 $x_i$ is a \textit{full contact} node, meaning that $u = \chi$ on
 $\omega_i = \cup_{T \mid x_i \in T} T$ the patch around $v$. Further,
 we need to have $|\omega_i| = \int_{\omega_i} \phi_i\,\mathrm{d}x$ for all
 vertices to correctly scale the complementarity residual.
 Unfortunately, both data are non-local, i.e., we can not compute it
 on any given $T$ alone.
